### 2023-11-07 main.tex
^
^^

\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These labels are defined in order to $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ are such that $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$. Therefore, we have 

@@

 \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. We this notation we have that 

>>>>

\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$. Therefore, we have 

@@

 \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. Thus, we have that 
